Processing of raw data

### 2022-03-08 01-processing-raw-data_reviews.Rmd
fix typo
get rid of excess whitespace in review text

# Chrome Web store
## Extract reviews from page sources
In this case, we've store .RDS files that contain the page sources.

@@

chrome_reviews %>% 
  # add date
  mutate(date_modified = str_remove(date_modified, "Modified "),
         date_modified = case_when(
          str_detect(date_modified, "hours ago") ~ "Feb 8, 2019",
          str_detect(date_modified, "1 day ago") ~ "Feb 7, 2019",
          str_detect(date_modified, "2 days ago") ~ "Feb 6, 2019",
          str_detect(date_modified, "3 days ago") ~ "Feb 5, 2019",
          str_detect(date_modified, "4 days ago") ~ "Feb 4, 2019",
          str_detect(date_modified, "5 days ago") ~ "Feb 3, 2019",
          str_detect(date_modified, "6 days ago") ~ "Feb 2, 2019",
          TRUE ~ date_modified
        ),
    date_modified = lubridate::mdy(date_modified)) %>% 
  rename(rating = numstars) %>% 
  distinct(across(-review_page)) %>% 
  write_csv(here::here("data", "processed", "chrome", "2019-02-08-chrome_reviews_unique.csv"))

@@

```{r}
play_reviews_tibble %>% 
  mutate(date = lubridate::mdy(date)) %>% 
  distinct() %>% 
  write_csv(here::here("data", "processed", "play", "2019_03_19-play_reviews_unique.csv"))

@@

# put 'em all in one big happy unnested tibble
apple_review_tibble <- apple_reviews %>% 
  mutate(review_info = map(reviews, extract_apple_review_info)) %>% 
  select(-reviews) %>% 
  unnest()

@@

```{r}
apple_reviews_all %>% 
  # merge the title of the apple reviews into the text, then remove line breaks
  mutate(user_name = str_remove(user_name, "\n"),
         review_text = str_c(review_title, review_text, sep = ". ") %>% str_replace_all("\n", "")) %>% 
  select(-review_title) %>% 
  # turn the rating into an integer
  mutate(rating = str_replace(rating, "out of 5", "") %>% as.integer()) %>% 
  # change date format
  mutate(date = lubridate::dmy(date)) %>% 
  distinct() %>% 
  write_csv(here::here("data", "processed", "apple", "2019-03-21_apple_reviews_unique.csv"))
```

>>>>

# Chrome Web store
## Extract reviews from page sources
In this case, we've stored .RDS files that contain the page sources.

@@

chrome_reviews %>% 
  # add date
  mutate(date_modified = str_remove(date_modified, "Modified "),
         date_modified = case_when(
          str_detect(date_modified, "hours ago") ~ "Feb 8, 2019",
          str_detect(date_modified, "1 day ago") ~ "Feb 7, 2019",
          str_detect(date_modified, "2 days ago") ~ "Feb 6, 2019",
          str_detect(date_modified, "3 days ago") ~ "Feb 5, 2019",
          str_detect(date_modified, "4 days ago") ~ "Feb 4, 2019",
          str_detect(date_modified, "5 days ago") ~ "Feb 3, 2019",
          str_detect(date_modified, "6 days ago") ~ "Feb 2, 2019",
          TRUE ~ date_modified
        ),
    date_modified = lubridate::mdy(date_modified)) %>% 
  rename(rating = numstars) %>% 
  mutate(text = str_squish(text)) %>% # get rid of excess whitespace 
  distinct(across(-review_page)) %>% 
  write_csv(here::here("data", "processed", "chrome", "2019-02-08-chrome_reviews_unique.csv"))

@@

```{r}
play_reviews_tibble %>% 
  mutate(date = lubridate::mdy(date),
         text = str_squish(text)) %>% 
  distinct() %>% 
  write_csv(here::here("data", "processed", "play", "2019_03_19-play_reviews_unique.csv"))

@@

# put 'em all in one big happy unnested tibble
apple_review_tibble <- apple_reviews %>% 
  mutate(review_info = map(reviews, extract_apple_review_info)) %>% 
  select(-reviews) %>% 
  unnest(cols = c(review_info))

@@

```{r}
apple_reviews_all %>% 
  # merge the title of the apple reviews into the text, then remove line breaks
  mutate(user_name = str_remove(user_name, "\n"),
         review_text = str_c(review_title, review_text, sep = ". ") %>% str_replace_all("\n", "")) %>% 
  select(-review_title) %>% 
  # turn the rating into an integer and change date format
  mutate(rating = str_replace(rating, "out of 5", "") %>% as.integer(),
         date = lubridate::dmy(date)) %>% 
  # get rid of excess whitespace
  mutate(review_text = str_squish(review_text)) %>% 
  distinct() %>% 
  write_csv(here::here("data", "processed", "apple", "2019-03-21_apple_reviews_unique.csv"))
```
